Staged Abstract Interpreters

### 2019-08-15 paper/10_intro.tex
at sign

The idea of specializing interpreters can be traced to Futamura
projections \cite{Futamura1999, futamura1971partial}.  The first
Futamura projection specifically shows that specializing an
interpreter w.r.t. the input program yields an equivalent
executable. For instance, @eval@ is an interpreter for some language:
\begin{lstlisting}
  def eval(e: Expr)(arg: Input): Value
\end{lstlisting}
Given a program $e_0$ of type @Expr@, by applying the specialization,
we can obtain a specialized interpreter $\texttt{eval}_{\texttt{e0}}$
: @Input@ $\to$ @Value@, which is the so-called \textit{equivalent
  executable}.  By definition of the interpreter, they produce the
same result when applied with the argument
$\texttt{eval}_{\texttt{e0}}(arg) = [\![ e_0 ]\!] arg $.

>>>>

The idea of specializing interpreters can be traced to Futamura
projections \cite{Futamura1999, futamura1971partial}.  The first
Futamura projection specifically shows that specializing an
interpreter w.r.t. the input program yields an equivalent
executable. For instance, \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{eval} is an interpreter for some language:
\begin{lstlisting}
  def eval(e: Expr)(arg: Input): Value
\end{lstlisting}
Given a program $e_0$ of type \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{Expr}, by applying the specialization,
we can obtain a specialized interpreter $\texttt{eval}_{\texttt{e0}}$
: \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{Input} $\to$ \lstinline[keywordstyle=,flexiblecolumns=false,mathescape=false,basicstyle=\tt]{Value}, which is the so-called \textit{equivalent
  executable}.  By definition of the interpreter, they produce the
same result when applied with the argument
$\texttt{eval}_{\texttt{e0}}(arg) = [\![ e_0 ]\!] arg $.
